Models

### 2024-03-18 analysis/05_model_metrics.Rmd
tweaks, update output

There are 12 study/metric combos that can't be fit due to data limitations (too many rarefyID's )
```{r}
tofit_mods <- bad_indv_results2 %>% filter(!is.na(warning)) %>% select(metric, study_id, formula) %>% distinct()

@@

#supplement of complete model output
bind_rows(metric_model_table, indv_mod_table) %>%
    select(-c(model_id, n_ts, warning, lower.CL, upper.CL, significant, REML, bobyqa)) %>%
  readr::write_csv(here::here("paper", "model_estimates_supp.csv"))

>>>>

There are 13 study/metric combos that can't be fit due to data limitations (too many rarefyID's )
```{r}
tofit_mods <- bad_indv_results2 %>% filter(!is.na(warning)) %>% select(metric, study_id, formula) %>% distinct()

@@

#supplement of complete model output
bind_rows(metric_model_table, indv_mod_table) %>%
    select(-c(n_ts, warning, lower.CL, upper.CL, significant, REML, bobyqa)) %>%
  readr::write_csv(here::here("paper", "model_estimates_supp.csv"))
